---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# committee_assigment


The goal of committee_assigment is to expedite the creation of *balanced* committee assignments given a handful of *constraints*.

This is achieved by using the `{GA}` package to run a genetic algorithim and optimize
committee assignments.

## Objectives & Constraints

The main objective is to create balanced committee assignments that represent the 
overall population as whole.  This means controlling for certain variables, such as 
gender, occupation, region, etc.

The largest constraint are:

* Gender (ensure balanced gender representation)
  * Goal is 50% Female /  50% Male (this was a basic demo that ignores other gender identities (i.e. non-binary))
* Job (ensure each Job role is equally represented)
  * Goal is 25% each category
  * Large penalty applied if any Job is less than 15% of committee
* Region (ensure representation from each region, try to balance it)
  * Goal is 9% per region
  * Large penalty applied if any region is not represented at all

## Using this repo

This project was setup with the `{checkpoint}`  for package versioning.  It's not perfect
but it works.  You can activate the checkpoint folder by running the `utils\project_setup.R` file.
More details on project development environment is listed belowin the `Session Info` section.

The `utils\ga_helpers.R` file has all the functions used in genetic algorithim.

The `utils\generate_fake_data.R` file is a temp file purely for development.  It, as
the name suggests, generates fake data to demo how the process **could** work.

## Session Info
```{r}
sessionInfo()
```


